\documentclass[10pt,a4paper]{extarticle}
\pagenumbering{gobble}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{graphicx}
\titleformat{\section}{\large\bfseries\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}
\begin{document}
\begin{center}
    \begin{minipage}{\textwidth}
        \centering
        {\LARGE\textbf{Enes Orhan}} \hspace{2pt} {\LARGE{Mobile \& Full-Stack Developer}}\\[10pt]
        \href{mailto:enesorhann404@gmail.com}{enesorhann404@gmail.com} \textbullet\
        \href{https://github.com/enesorhann}{github.com/enesorhann} \textbullet\
        \href{https://linkedin.com/in/enesorhann}{linkedin.com/in/enesorhann}
    \end{minipage}
\end{center}
\section{Summary}
I am an enthusiastic developer experienced in Flutter, Python and modern web technologies. I have built mobile and web applications end-to-end, including Bandox, a Kanban-based task management app using Flutter and Firebase, and other personal projects with RESTful APIs and PostgreSQL. I aim to further develop my skills and contribute to innovative software solutions.
\section{Experience}
\textbf{Fiyator A.Ş. \textit{(Konya, Türkiye)}} \hfill On-site\\
\textit{Software Development Intern} \hfill June 2025 -- August 2025
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Worked on backend development using Python (Django) and PostgreSQL with REST API.
    \item Contributed to mobile app features in Flutter, implementing Bloc pattern and Firebase integrations.
    \item Collaborated with team on Git and Jira for agile workflow.
\end{itemize}
\textbf{Bandox Project} \hfill Remote\\
\textit{Founder \& Developer} \hfill September 2024 -- June 2025
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Developed Bandox, a Kanban-based task and project management application using Flutter and Firebase.
    \item Built features such as drag-and-drop task board, department-based task assignment, chat and file sharing.
    \item Designed an admin panel for managing company data and integrated user authentication (Google Sign-In, email/password).
\end{itemize}
\textbf{Other Projects} \hfill Remote\\
\textit{Personal Developer} \hfill 2023 -- Present
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Built a mail client app with attachment preview and sending support.
    \item Developed a ToDo app using Flutter frontend and FastAPI backend with PostgreSQL.
    \item Worked on ML projects like diabetes prediction and job application evaluation using Decision Trees.
\end{itemize}
\section{Skills}
\textbf{Programming Languages:} Dart (Flutter), Python, Java, Kotlin\\
\textbf{Backend Frameworks \& Runtimes:} Django, FastAPI, Node.js\\
\textbf{Frontend Frameworks \& Runtimes:} Flutter, React.js (basic)\\
\textbf{Databases:} Firebase Firestore, PostgreSQL, MySQL\\
\textbf{Other:} Git, REST API, Docker (basic), Jira, Bloc Pattern, Firebase Auth, Cloud Storage
\section{Education}
\textbf{Konya Technical University} \hfill Konya, Türkiye\\
\textit{B.Sc. in Computer Engineering} \hfill September 2022 -- June 2026
\section{Scholarships}
\textbf{TÜBİTAK} \hfill Türkiye\\
\textit{Scholarship Holder, Researcher} \hfill April 2023 -- October 2023
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item Participated in the BİÇABA Scholarship Program with a deep learning project on X-Ray image analysis.
\end{itemize}
\end{document}
